Model \& Simulation of South Bend Government Call Center using Arena

### 2018-10-21 Paper.tex
Distributions for arrivals by hour and duration done.  Plots for paper done.  Some random paper cleanup too.
fix bib

\documentclass[12pt,twocolumn]{article}
\usepackage{graphicx}
\usepackage{pdfpages}
\usepackage{hyperref}
\usepackage[margin=1.25in]{geometry}
\usepackage[utf8]{inputenc}
\graphicspath{ {./Figures/} }
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}
\urlstyle{same}
\usepackage[font={small,it}]{caption}
\usepackage{fancyvrb}
\title{Model \& Simulation of South Bend Government Call Center using Arena}
\author{John D. Bulger, Jacob D. White \& Adali J.J. Johnson\\Valparaiso University\thanks{``We have neither given or received, nor have we tolerated other’s use of unauthorized aid."}}
\date{October 23, 2018}

@@

\par
The city's call center is seeking to explore XXXXX.  As such, this model and simulation will be constructed with the primary purpose of discovering an answer to this question in order to aid management's decision-making.  The call center will be modeled in Arena, as a discrete-event model, using the open-source data.  Through simulation, this question will be explored and answered.

\section{Background \& Terminology}
Call centers are a frequently studied topic within the simulation and modeling disciplines.  As such, some basic terminology shall be explained.  This model consists of two primary components:  calls and operators.  Calls will be represented as entities in Arena, as they are created and move through the system.  For this exploration, an ``arrival" is defined as a unique call first coming into the call process model.  The operators, also known as ``311 liasons," will be represented as resources in Arena.
\par
%more here
We need another background paragraph here
%more here

\section{Prior Work}

Call center and queuing analysis has been the focus of academic research for years.  Brown et al. provide an excellent overview of the Poisson distribution modeling customer arrivals, as well as the accompanying assumptions.  While arrival distribution is analyzed directly from the data in this model, the authors' assumptions are, for the most part, assumed to be true in this analysis.  These center around the general assumption that the customers and operators are statistically identical and that they all act independently.\cite{brown}  Zhang, Hong, and Zhang also describe the arrival process as a Poisson distribution, but discuss models which may be more accurate alternatives.\cite{zhang}  They maintain some of the main assumptions as Brown.  As a result, differences in time-dependent parameters, customer attitudes and preferences, and operator skill levels are treated as negligible.
\par
Call centers are a prime opportunity to utilize simulation techniques.  In fact, according to Bapat and Pruitte, simulation is the preferred method to analyze and determine the effectiveness of a call center.\cite{bapat}  It allows for evaluation of metrics beyond what a basic analysis encompasses.  For example, the scheduling of call agents should be optimized against call duration and abandonment, as documented by Saltzman and Mehrota.\cite{saltzman}  Such simulations can easily be created to illustrate feasibility of goal accomplishment for corporations while enabling efficient and accurate decision-making.\cite{saltzmeh}

@@

% I need to rework all of this shit
While such arrivals are frequently defined with an exponential distribution, this model utilizes a more accurate representation of arrivals as calculated from the aforementioned open-source data.  The scheduling of operators (resources) is dedicated by the actual 311 call center schedule, showing in Figure 3.

@@

While these calls move through the model, they will undergo several assignments, in which they are assigned a priority, language, and topic.  The topic will determine the duration distribution as identified from the open-source data, and the language (English or Spanish) will determine into which operator queue.  Calls will then enter a queue until they can speak to an agent.  After completing or abandoning the calls, the entity is referred to as ``disposed" since it leaves the model at that time.

@@

\section{Challenges}

@@

\newpage
\clearpage
\begin{thebibliography}{7}
\bibitem{baraka}
Baraka, H., Baraka H. \& El-Gamily, I. (2013). Assessing call centers' success: A validation of the DeLone and Mclean model for information system. \textit{Egyptian Informatics Journal, 14}, 99-108.

@@

\bibitem{zhang}
Zhang X., L. Jeff Hong, \& Jiheng Zhang. (2014). Scaling and modeling of call center arrivals. \textit{In Proceedings of the 2014 Winter Simulation Conference (WSC '14)}. IEEE Press, Piscataway, NJ, USA, 476-485.

\bibitem{saltzman}
Saltzman, R. \& Mehrotra, V.. (2007). Managing trade-offs in call center agent scheduling: methodology and case study. \textit{In Proceedings of the 2007 Summer Computer Simulation Conference (SCSC '07)}. Society for Computer Simulation International, San Diego, CA, USA, 643-651.

\bibitem{mandelbaun}
Mandelbaun A., A. Sakov and S. Zeltyn. (2001). Empirical Analysis of a Call Center. Technion Israel Institute of Technology, Israel.

>>>>

\documentclass[12pt,twocolumn]{article}
\usepackage{graphicx}
\usepackage{pdfpages}
\usepackage{hyperref}
\usepackage[margin=1.25in]{geometry}
\usepackage[utf8]{inputenc}
\graphicspath{ {./Figures/} }
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}
\urlstyle{same}
\usepackage[font={small,it}]{caption}
\usepackage{fancyvrb}
\title{Model \& Simulation of South Bend Government Call Center using Arena}
\author{John D. Bulger, Jacob D. White \& Adali J.J. Johnson\\Valparaiso University\thanks{``We have neither given or received, nor have we tolerated others' use of unauthorized aid."}}
\date{October 23, 2018}

@@

\par
The city's call center is seeking to explore operational efficiency with regard to operator staff.  As such, this model and simulation will be constructed with the primary purpose of discovering the optimal number of agents while maintaining adequate customer satisfaction (measured by time in queue).  Additionally, the model will be modified to explore the addition of a self-service touch-tone option that would allow for callers to complete simple tasks, such as scheduling an extra trash pickup, without speaking to an agent.  Through simulation, these questions were be explored and solved.  The open-source data was processed in Python in order to extract relevant distributions, and the call center was modeled in Arena as a discrete-event model.

\section{Background}
Call centers are a frequently studied topic within the simulation and modeling disciplines.  As such, some basic terminology shall be explained.  This model consists of two primary components:  calls and operators.  Calls will be represented as entities in Arena, as they are created and move through the system.  For this exploration, an ``arrival" is defined as a unique call first coming into the call process model.  The operators, also known as ``311 liasons," will be represented as resources in Arena.

	\subsection{Prior Work}

Call centers are a prime opportunity to utilize simulation techniques.  In fact, according to Bapat and Pruitte, simulation is the preferred method to analyze and determine the effectiveness of a call center.\cite{bapat}  It allows for evaluation of metrics beyond what a basic analysis encompasses.  For example, the scheduling of call agents should be optimized against call duration and abandonment, as documented by Saltzman and Mehrota.\cite{saltzman}  Such simulations can easily be created to illustrate feasibility of goal accomplishment for corporations while enabling efficient and accurate decision-making.\cite{saltzmeh}

Call center and queuing analysis has been the focus of academic research for years.  Brown et al. provide an excellent overview of the Poisson distribution modeling customer arrivals, as well as the accompanying assumptions.  While arrival distribution is analyzed directly from the data in this model, it will still be implemented as an hourly Poisson distribution. In order to implement this arrival methodology, the authors maintain assumptions that the customers and operators are statistically identical and that they all act independently.\cite{brown}  Zhang, Hong, and Zhang also describe the arrival process as a Poisson distribution, but discuss models which may be more accurate alternatives.\cite{zhang}  They maintain some of the main assumptions as Brown.  Additionally, they point out that differences in time-dependent parameters, customer attitudes and preferences, and operator skill levels should treated as negligible.

@@

The model used for this analysis expands a great deal on the core model identified by Mandelbaun.  In addition to arriving calls, voicemails are ``created" as soon as each simulation ''day" begins, so that the call center has all day to return those calls.  Additionally, some calls get routed to a supervisor after speaking with an agent.  This supervisor resource can then resolve the call, or pass it back to an agent.  This was added in an attempt to model actual call center behavior, where some callers may need assistance beyond a basic agent.  As calls and voicemails arrive and flow through the model, they are assigned three key attributes: topic, language, and priority.

\paragraph{Topic}

Calls are assigned a topic based on the distribution of topics in historical call center data.  In an effort to preserve the simplicity of the model while still utilizing past data, the top six departments (by total number of calls) are specified, with the remaining calls grouped into an ''other" category.  By assigning a topic, the simulation will be able to utilize the historical means and standard deviations of those topics' call durations in order to most accurately replicate the call center.  The departments specifically included in the model account for 90\% of the total call volumes, while the ``other" category constitutes the remaining 10\%.

\paragraph{Language}

Each call and voicemail is assigned a language of either Spanish or English.  The actual call center deals in both of those language, and it has Spanish-speaking operators available.  In order to reflect this, the model's resources all speak English, with some able to speak Spanish as well.  Therefore, arrivals will be routed into two queues:  one for English, and one for Spanish.

\paragraph{Priority}

All incoming calls are assigned a medium priority by default, and voicemails are given the lowest priority (as they can be answered and returned as time permits).  After speaking to an agent, calls needing escalation to a supervisor are given the highest priority (in the event they need to cycle back through the queue again).

	\subsection{Verification Techniques}

	\subsection{Validation Plan}

	\subsection{Base Simulation Setup}
This simulation utilizes an accurate representation of arrivals as calculated from the aforementioned open-source data.  Mean call arrivals were identified down to the hour for each weekday.  The results allows for the arrivals to be scheduled as such in Arena.  This will base the actual volume of calls in line with prior historical trends, as opposed to applying a rough blanket estimate.  The scheduling of operators (resources) is also dictated by historical data.  The operator schedule was supplied by call center management.  This schedule can be seen in Figure 3.

@@

@@

@@

\section{Conclusion}

	\subsection{Challenges}

	\subsection{Opportunities for Further Study}

\newpage
\clearpage
\pagenumbering{gobble}
\begin{thebibliography}{7}

	\bibitem{saltzman}
	Saltzman, R.M. \& Mehrotra, V.. (2007). Managing trade-offs in call center agent scheduling: methodology and case study. \textit{In Proceedings of the 2007 Summer Computer Simulation Conference (SCSC '07)}. Society for Computer Simulation International, San Diego, CA, USA, 643-651.

	\bibitem{baraka}
	Baraka, H., Baraka H. \& El-Gamily, I. (2013). Assessing call centers' success: A validation of the DeLone and Mclean model for information system. \textit{Egyptian Informatics Journal, 14}, 99-108.

@@

	\bibitem{zhang}
	Zhang X., Jeff Hong L., \& Zhang J.. (2014). Scaling and modeling of call center arrivals. \textit{In Proceedings of the 2014 Winter Simulation Conference (WSC '14)}. IEEE Press, Piscataway, NJ, USA, 476-485.

	\bibitem{mandelbaun}
	Mandelbaun A., Sakov A., \& Zeltyn S.. (2001). Empirical Analysis of a Call Center. Technion Israel Institute of Technology, Israel.
